### 2015-12-23 Projects/Exploratory_Convective_PPE/Report/convective_ppe_heating.tex
update convective report and bib file

\begin{tabbing}
\hspace{1.5in} \= \\
NIST \> National Institute of Standards and Technology \\
\end{tabbing}

@@

\chapter*{\centering Abstract}
\pagenumbering{gobble}
The overall objective of this interagency agreement between the United States Fire Administration (USFA) and the National Institute of Standards and Technology (NIST) is to would be to fill that data gap to better define the thermal limits of the operational fire environment its impact on structural firefighting PPE and deliver this information to the appropriate standards groups and the fire service.  Without an accurate understanding of the conditions of environments in which a firefighter can safely operate, firefighters are more at risk of injuries and death.
To accomplish this, NIST will examine documented on-duty injuries and fatalities of firefighters due to thermal exposure of PPE used by structural firefighters.  Further NIST will conduct laboratory thermal testing of commercially available this PPE as part of this phase of the study.

Tasks:

1.	NIST shall examine documented on-duty injuries and fatalities of firefighters due to thermal exposure of structural firefighting PPE.    (LIST)

2.	NIST shall conduct laboratory thermal testing of commercially available structural firefighting PPE as part of this phase of the study, with a focus on convective heat transfer.  The testing shall include any relevant performance requirements for structural firefighting PPE thermal exposure in NFPA 1971.   Plunge Test $\&$ Flow Loop

3.	NIST shall conduct full-scale thermal testing of structural firefighting PPE at field test sites.  Field testing will be coordinated with the COR.

>>>>

\begin{tabbing}
\hspace{1.5in} \= \\
NIST \> National Institute of Standards and Technology \\
PPE \> Personal Protective Equipment \\
\end{tabbing}

@@

\chapter*{\centering Abstract}
\pagenumbering{gobble}
The overall objective of this interagency agreement between the United States Fire Administration (USFA) and the National Institute of Standards and Technology (NIST) is to better define the thermal limits of the operational fire environment, its impact on structural firefighting personal protective equipment (PPE), and deliver this information to the appropriate standards groups and the fire service.  Without an accurate understanding of the conditions of environments in which a firefighter can safely operate, firefighters are more at risk of injuries and death.

To accomplish this, NIST will examine documented on-duty injuries and fatalities of firefighters due to thermal exposure of PPE used by structural firefighters.  Further NIST will conduct laboratory thermal testing of commercially available PPE as part of this phase of the study:
\begin{enumerate}
\item NIST shall examine documented on-duty injuries and fatalities of firefighters due to thermal exposure of structural firefighting PPE \cite{Weinschenk:Chicago,Overholt:San_Francisco,Weinschenk:PGCounty}.
\item NIST shall conduct laboratory thermal testing of commercially available structural firefighting PPE as part of this phase of the study, with a focus on convective heat transfer.  The testing shall include any relevant performance requirements for structural firefighting PPE thermal exposure in NFPA 1971.
\item NIST shall conduct full-scale thermal testing of structural firefighting PPE at field test sites.
